\mytitle

### 2015-08-05 MSc_diss.tex
Updates in section about O3 and groups of ANs

\section{Results} \label{sec:res}
\subsection{Sensitivity of $O_3$ production to alkyl nitrate chemistry}\label{sec:res_O3ANsensetivity}

@@

As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the difference in $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3mixrat noAN allAN diff diffpercent
\centering
\begin{minipage}{.4\textwidth} % noAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diff
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % allAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diffpercent
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiffpercent_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb, range 250 ppt - 100 ppb) with alkyl nitrate chemistry switched off (a) and switched on (b). Absolute difference (with alkyl nitrates minus without them) between two series of model runs in ppb (c), same in \% (d). Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\section{Results} \label{sec:res}
\subsection{Sensitivity of $O_3$ production to alkyl nitrate chemistry}\label{sec:res_O3ANsensetivity}
\subsubsection{$O_3$ and total alkyl nitrates}

@@

As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the difference in $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3mixrat noAN allAN diff diffpercent
\centering
\begin{minipage}{.4\textwidth} % noAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diff
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % allAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diffpercent
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiffpercent_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb, range 250 ppt - 100 ppb) with alkyl nitrate chemistry switched off (a) and switched on (b). Absolute difference (with alkyl nitrates minus without them) between two series of model runs in ppb (c), same in \% (d). Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{$O_3$ and individual alkyl nitrates}

To estimate the impact of individual alkyl nitrates or their groups on $O_3$ production an additional series of experiments have been conducted (Figure \ref{fig:timeO3diff10ppbNOx6VOC}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_timeO3diff_10ppbNOx6VOC.eps}
\caption{Time evolution of the difference in $O_3$ mixing ratio between base experiment (with all alkyl nitrate chemistry switched on) and experiments where chemistry of individual alkyl nitrates or their groups is switch on. Black line shows the difference between base experiment and an experiment with all alkyl nitrate chemistry switched off. $NO_x$ = 10 ppb, $VOCs$ = case F.}\label{fig:timeO3diff10ppbNOx6VOC}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{Difference in $O_3$ mixing ratio by the end of simulation depending alkyl nitrate chemistry.}\label{tab:timeO3diff10ppbNOx6VOC}
\begin{tabular}{cc}
\hline
Alkyl nitrate            & $O_3$ difference (ppb) \\
\hline
$CH_3ONO_2$              & -11.5 \\
$C_2H_5ONO_2$            & -11.6 \\
$\Sigma C_3H7ONO_2$      & -10.5 \\
$\Sigma nC_4H_9ONO_2$    & -8.7  \\
$\Sigma iC_4H_9ONO_2$    & -11.0 \\
$\Sigma nC_5H_{11}ONO_2$ & -10.1 \\
$\Sigma iC_5H_{11}ONO_2$ & -8.0  \\
$\Sigma RONO_2$          & -11.9 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
